Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-01-28 content.tex
Updates from Overleaf

\begin{sidewaystable}
\centering
  \begin{tabular}{|p{3.4cm}|p{9.7cm}|p{4.5cm}@{}|}
    \hline
    \centering
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{Sub-argument} & 
    \textbf{Description} &
    \textbf{Possible values} \\ 
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;tree_prior; &
    Macroevolutionary diversification model &
    Yule, BD, CBS, CCP, CEP \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;clock_model; &
    Clock for the DNA mutation rates &
    strict, RLN \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;site_model; &
    Nucleotide substitution model &
    JC, HKY, TN93, GTR \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;mutation_rate; &
    Pace at which mutation occurs &
    \verb;mutation_rate; $\in \mathbb{R}_{>0}$\\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;root_sequence; &
    DNA sequence at the root of the tree &
    any combination of a, c, g, t \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;model_type; &
    Criterion to select an inference model &
    Generative, Candidate \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;run_if; &
    Condition under which an inference model is used &
    Always, Best candidate \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;do_measure_evidence; &
    Sets whether or not the evidence of the model is to be computed &
    TRUE, FALSE \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;error_fun; &
    Specifies how to measure the error &
    nLTT, $|\gamma|$ \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;burn_in_fraction; &
    Specifies the percentage of initial posterior trees to discard &
    \verb;burn_in_fraction; $\in [0, 1]$\\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline
  \end{tabular}
  \caption{
    Most important parameter options.
    Yule = pure birth model (\cite{yule})
    BD = birth death (\cite{nee1994reconstructed}), 
    CBS = coalescent Bayesian skyline (\cite{drummond2005bayesian}), 
    CCP = coalescent constant-population, 
    CEP = coalescent exponential-population,
    JC = Jukes and Cantor (\cite{jukes1969evolution}), 
    HKY = Hasegawa, Kishino and Yano (\cite{hasegawa1985dating}), 
    TN93 = Tamura and Nei (\cite{tamura1993estimation}), 
    GTR = Generalized time-reversible model (\cite{tavare1986some})
    RLN = relaxed log-normal clock model (\cite{drummond2006relaxed}).
  }
  \label{tab:options}
\bigskip

>>>>

\begin{sidewaystable}
\centering
  \begin{tabular}{|p{3.4cm}|p{9.7cm}|p{4.5cm}@{}|}
    \hline
    \centering
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{Sub-argument} & 
    \textbf{Description} &
    \textbf{Possible values} \\ 
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;tree_prior; &
    Macroevolutionary diversification model &
    Yule, BD, CBS, CCP, CEP \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;clock_model; &
    Clock for the DNA mutation rates &
    strict, RLN \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;site_model; &
    Nucleotide substitution model &
    JC, HKY, TN93, GTR \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;mutation_rate; &
    Pace at which mutation occurs &
    \verb;mutation_rate; $\in \mathbb{R}_{>0}$\\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;root_sequence; &
    DNA sequence at the root of the tree &
    any combination of a, c, g, t \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;model_type; &
    Criterion to select an inference model &
    Generative, Candidate \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;run_if; &
    Condition under which an inference model is used &
    Always, Best candidate \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;do_measure_evidence; &
    Sets whether or not the evidence of the model is to be computed &
    TRUE, FALSE \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;error_fun; &
    Specifies how to measure the error &
    nLTT, $|\gamma|$ \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \verb;burn_in_fraction; &
    Specifies the percentage of initial posterior trees to discard &
    \verb;burn_in_fraction; $\in [0, 1]$\\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline
  \end{tabular}
  \caption{
    Most important parameter options.
    Yule = pure birth model (\cite{yule})
    BD = birth death (\cite{nee1994reconstructed}), 
    CBS = coalescent Bayesian skyline (\cite{drummond2005bayesian}), 
    CCP = coalescent constant-population, 
    CEP = coalescent exponential-population,
    strict = strict clock model (\cite{zuckerkandl1965molecules}),
    RLN = relaxed log-normal clock model (\cite{drummond2006relaxed}),
    JC = Jukes and Cantor (\cite{jukes1969evolution}), 
    HKY = Hasegawa, Kishino and Yano (\cite{hasegawa1985dating}), 
    TN93 = Tamura and Nei (\cite{tamura1993estimation}), 
    GTR = Generalized time-reversible model (\cite{tavare1986some}).
  }
  \label{tab:options}
\bigskip
